Planar Maximal Covering with Ellipses

### 2019-05-01 quali/quali.presentation/slides.tex
WIP

\newcommand{\bigO}{\mathscr{O}}

\usepackage{pgfplots}
\pgfplotsset{compat=1.4}
\usepackage{algorithm2e}
\usepackage{algorithmic}
\usepackage{float}
\usepackage{caption}
\newcommand{\source}[1]{\caption*{Source: {#1}} }

@@

\section{Introduction}
\begin{frame}
\frametitle{Introduction}
\begin{itemize}
	\item Covering problems
	\begin{itemize}
		\item Set Cover Problem
		\item Maximal Covering Problem
	\end{itemize}
	\item Maximal Covering Location Problem (MCLP)
	\item Planar Maximal Covering Location Problem (PMCLP)
	\begin{itemize}
	\item One disk: $\bigO(n^2)$ and $\bigO(n^2\log{n})$ algorithms
	\item $m$ disks: $\bigO(n^{2m-1}\log{n})$ algorithm
	\end{itemize}
	\item Goals
	\begin{itemize}
		\item Develop a $\bigO(n^2\log{n})$ algorithm for the one disk case
		\item Adapt it for the $m$ ellipses case
	\end{itemize}
\end{itemize}

@@

@@

		\caption{The elliptical and euclidean norms}
		\input{figures/elliptical.and.euclidean.norms.tex}
		\source{Elaborated by the author.}
		\label{fig:3ellipses_intersect}

@@

		\caption{An instance of $MCD(\Pp,1)$.}
		%\input{figures/elliptical.and.euclidean.norms.tex}
      \center{\includegraphics[width=.7\textwidth]{figures/mcd_instance.png}}
		\source{Elaborated by the author.}
		\label{fig:mcd_instance}
	\end{figure}
\end{frame}

		\caption{An instance of Maximum Weight Clique Problem.}
		%\input{figures/elliptical.and.euclidean.norms.tex}
		\center{\includegraphics[width=.7\textwidth]{figures/mwc_instance.png}}
		\source{Elaborated by the author.}
		\label{fig:max_wieght_clique}
	\end{figure}
\end{frame}

\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
	Let $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ be the opening and closing angles (with respect to $D_i$) of intersections of disks $i$ and $j$. Also, $\Gamma_+(i,j), \Gamma_-(i,j) \in [0,2\pi]$.
	\begin{figure}[H]
		\centering

		\caption{Three disks and their intersection points.}
		\input{figures/img2.tex}
		\source{Elaborated by the author.}
		\label{fig:3disks_intersect}
	\end{figure}
\end{frame}

@@

		\item In a counter-clockwise traversal, the arcs where $\Gamma_+(i,j) > \Gamma_-(i,j)$ can be a problem for the implementation. Work-around: repeat it.
	\end{itemize}
\end{frame}

@@

	The algorithm is described simply as:

@@

@@

\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
\begin{figure}
	%\centering

	\caption{A traversal for $D_1$ with green disks representing the active set and red signs representing the current angle being visited (some are omitted).}
	\input{figures/mcd_sim.tex}
		\source{Elaborated by the author.}
	%\label{fig:array_disks}
\end{figure}
\end{frame}

@@

\begin{frame}{Maximum Weight Clique Problem}{Multiple disks}
	\begin{itemize}
		\item In \cite{cabello:2006} a $\bigO(n^{2m-1})$ algorithm was proposed. Also a $(1-\epsilon)-$approximation that runs in $\bigO(n\log{n})$ was introduced.

@@

>>>>

\newcommand{\bigO}{\mathscr{O}}
\usetikzlibrary{matrix}
\usepackage{pgfplots}
\pgfplotsset{compat=1.4}
\usepackage{algorithm2e}
\usepackage{algorithmic}
\usepackage{float}
\usepackage{caption}
\newcommand{\source}[1]{\caption*{Source: {#1}} }

@@

\section{Introduction}
\begin{frame}
\frametitle{Introduction}
\begin{itemize}
	\item Covering problems
	\begin{itemize}
		\item Minimum Cover Problem
		\item Maximal Covering Problem
	\end{itemize}
	\item Maximal Covering Location Problem (MCLP)
	\item Planar Maximal Covering Location Problem (PMCLP)
	\begin{itemize}
	\item One disk: $\bigO(n^2)$ and $\bigO(n^2\log{n})$ algorithms
	\item $m$ disks: $\bigO(n^{2m-1}\log{n})$ algorithm
	\end{itemize}
	\item Goals
	\begin{itemize}
		\item Develop a $\bigO(n^2\log{n})$ algorithm for the one disk case
		\item Adapt it for the $m$ ellipses case creating a $\bigO(n^{2m})$ algorithm
	\end{itemize}
\end{itemize}

@@

\begin{frame}
	\begin{figure}
		\only<1>{\caption{Maximal cover by two disks.}}
		\only<2>{\caption{Minimum number of disks needed to cover the set of points.}}
		\only<1>{\input{figures/intro_a.tex}}
		\only<2>{\input{figures/intro_b.tex}}
		\source{Elaborated by the author.}
	\end{figure}
\end{frame}

@@

		\caption{The elliptical and euclidean norms.}
		\input{figures/elliptical.and.euclidean.norms.tex}
		\source{Elaborated by the author.}
		\label{fig:3ellipses_intersect}

@@

		\only<1>{\caption{An instance of the Maximum Weight Clique Problem obtained from an instance of $MCD(\Pp, 1)$.}}

		\only<2>{\caption{An instance of the Maximum Weight Clique Problem obtained from an instance of $MCD(\Pp, 1)$. In gray, the optimal solution.}}

		\only<1>{\input{figures/max_w_clique.tex}}
		\only<2>{\input{figures/max_w_clique_b.tex}}
      %\center{\includegraphics[width=.7\textwidth]{figures/mcd_instance.png}}
		\source{Elaborated by the author.}
		\label{fig:mcd_instance}
	\end{figure}
\end{frame}

\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
	Defining $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$:

	Let $D_i$ and $D_j$ be two unit disks that intersect at two points.

	\begin{itemize}
		\item Assume $D_i$ is at the origin
		\item We can find the polar angle of the intersection points. Let's call them $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ with the following condition:
		\begin{itemize}
			\item The arc defined by $\Gamma_+(i,j)$ and $\Gamma_-(i,j)$ bounds the region $D_i \cap D_j$

		\end{itemize}
		\item Later it will be shown how to find which one is which algorithmically.
	\end{itemize}
\end{frame}

\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
	\begin{figure}[H]
		\centering

		\caption{Three disks and their intersection points and angles.}
		\input{figures/img2.tex}
		\source{Elaborated by the author.}
		\label{fig:3disks_intersect}
	\end{figure}
\end{frame}

@@

		\item In a counter-clockwise traversal, the arcs where $\Gamma_+(i,j) > \Gamma_-(i,j)$ can be a problem for the implementation. The traversal is on a circle, where to start?

		\item If the traversal reaches a opening angle, we mark the intersecting disk as active. If it reaches a closing angle we unmark it.

		\item We want to find a point in the traversal with the most active disks.
	\end{itemize}
\end{frame}

@@

@@

	Doing the traversal twice solves the problem of deciding where to start.

@@

%\begin{frame}{Maximum Weight Clique Problem}{Algorithm}
%\begin{figure}
	%\centering

%	\caption{A traversal for $D_1$ with green disks representing the active set and red signs representing the current angle being visited (some are omitted).}
%	\input{figures/mcd_sim.tex}
%		\source{Elaborated by the author.}
	%\label{fig:array_disks}
%\end{figure}
%\end{frame}

	\begin{figure}
		\caption{A traversal for $D_1$ with green disks representing the active set and red signs representing the current angle being visited (some are omitted).}
		\only<1>{\input{figures/mcd_sim_1.tex}}
		\only<2>{\input{figures/mcd_sim_2.tex}}
		\only<3>{\input{figures/mcd_sim_2_5.tex}}
		\only<4>{\input{figures/mcd_sim_3.tex}}
		\only<5>{\input{figures/mcd_sim_4.tex}}
		\only<6>{\input{figures/mcd_sim_5.tex}}
		\only<7>{\input{figures/mcd_sim_6.tex}}
		\only<8>{\input{figures/mcd_sim_7.tex}}
			\source{Elaborated by the author.}
	\end{figure}
\end{frame}

@@

\begin{frame}{Maximum Covering by Disks}{Multiple disks}

	Works found in the literature:

	\begin{itemize}
		\item In \cite{cabello:2006} a $\bigO(n^{2m-1})$ algorithm was proposed. Also a $(1-\epsilon)-$approximation that runs in $\bigO(n\log{n})$ was introduced.

@@

	Because of the similarities, we will discuss only the multiple ellipses algorithm later.
